%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Yudhishthir} % Your first name
\familyname{Raut} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Teaching and Research Statement}
\address{Yudhishthir Raut}{}
\mobile{(+91) 9009255611}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{r.yudhi@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Previous Research Experience}
My research aims to address the question, 'How best I can encode my medical modality so that it can be utilize in tele-medicine application as well as in PACS'. My past research has helped to answer this question by making novel compression techniques using HEVC/H.265 , and I have experience comparing with simulation as well as its quality analysis in objective and subjective type. However, in general I am interested in exploring the impact of compression in tele-medicine and broadcasting the UHD video content .

{\hskip 2em}Details of my previous research work are available in my CV, but I would like to highlight my interests in Medical imaging and its compression, still image and video compression. In analysis part I am interested in both objective analysis as well as subjective analysis of the content or modality.\\
%----------------------------------------------------------------------------------------
\section{Research Goals}
To work in the field of Image and video processing especially in the field of medical imaging analysis and diagnosis. The work may contain the acquisition and analysis for diagnostic of ailment or injury in the brain and its effect on human behaviour further moving forward for the tele-medicinal arena which is rarely explored.
To teach and develop the laboratory in the field of signal processing (including image and video processing) for UG and PG courses where learners (students also the faculties) can attain sufficient knowledge, motivation, and zeal for their respective courses.
To motivate students for Medical imaging and video analysis so that students can pursue Ph.D. under this area as this area deals with tele-medicine which is at present in an infancy stage. Also in addition to this, I would like to share my years of experience to guide students in their personality and development. Apart from above, I would also like to aid in the growth of the department in any manner if I can.  
I am looking to join an exciting and ambitious organization such as yours. I have an ability to grow with a job, handle responsibility and build positive relationships with work colleagues at all levels.
With eminent support like yours, I know that I will gain expert knowledge at the vanguard of discovery. Given my past history of commitment to excellence, I am confident that I will bring a high level of energy and enthusiasm to your organization. I am sure to exceed your anticipations, because of both my academic and interpersonal skills.

{\hskip 2em}You will find me to be well-spoken, energetic, confident, and personable. I am someone who knows how to set goals and achieve them and has a proven track record of being able to conceive, develop & execute strategies.
I am very much with hope that you will look favourable upon my application by recognizing my enthusiasm, talents and my future potential. I would highly appreciate the fact if you consider my application, review my credentials and discuss the possibilities further.
Furthermore, I recognize the importance of recruiting and mentoring graduate students to make my research plans a success. In particular, I am committed to responsible and safe conduction of research and to recruiting from a diverse pool of students. I plan to quickly develop positive working and mentoring relationships to enhance both my own and my student's success. %Particularly attractive is my knowledge of Michigan's dedication to interdisciplinary research aimed at solving high impact problems, and strong pool of undergraduates, graduate students, and faculty collaborators.
\section{Teaching}
My teaching interests span experiments in Digital signal processing, Digital Image processing Cellular and mobile communication and Wireless communication.  I won Srijan award in year 2015 for best result in university in Cellular and mobile communication. I won Achiever of the month award  in year 2012 for overall performance as employee in SIRT-Excellence, Bhopal. I secured merit position in Tech-guru awards in year 2017, a national level competition for engineering faculty to showcase their technical knowledge. While at Bhopal and Chirala (A.P.), I enjoy interactions with students, and look forward to inviting undergraduates from the classroom into the research lab. While I am able to teach a wider range of introductory courses at the undergraduate level if necessary, I would feel most comfortable starting in the areas of experimental and theoretical Signal processing. I feel I could teach the following courses with a high level of expertise:\\

$\bullet{}$ Undergraduate:Digital signal processing, Digital Image processing Cellular and mobile communication and wireless communication.\\
$\bullet{}$ Post Graduate: Bio-medical Engineering, Digital Image processing, Modeling and simulation.\\

{\hskip 2em}I believe that a comprehensive set of courses on Signal and system and bio-medical signal processing would be a worthwhile addition to a core competency at the undergraduate level. Drawing motivation from sustainable practices used aboard in the National Institute of Health (NIH), I am also interested in developing innovative courses that are applicable to sustainability in engineering. Finally, I propose an graduate level technical communications class. Topics would include giving technical presentations, and technical writing and reviewing, and an assignment to prepare an NSF-like fellowship grant proposal. The students will read current journal articles in their area of study, practice writing article reviews, and present summary (review) lectures on these advanced topics.  Although my experience is in the context of Bio-medical imaging and signal processing, the class could be thought of as graduate research program development as well as practice at professionalization for students.

{\hskip 2em}I cultivate the following attitudes in students who complete course work or research with me:

$\bullet{}$ Demonstrate understanding of rigorous mathematical tools for design/analysis,

$\bullet{}$ Exhibit audience driven communication strategies,

$\bullet{}$ Establish sound environmental/ethical/social reasoning.

\end{document}
